Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/JFLA2022/paper.tex
rephrase statement of Theorem 3

\begin{theorem}
  There is no termination measure mapping hydras to a segment $[0,\mu)$ where $\mu<\epsilon_0$ for proving the termination of  all hydra battles.\label{thm3}
\end{theorem}

>>>>

\begin{theorem}
  Let $\mu$ be any ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$, which could be used as a measure for  proving the termination of  all hydra battles.\label{thm3}
\end{theorem}
